Proportional multi-state multiple-cohort life table model

### 2018-04-10 MSLT/MSLTdoc.Rmd
Population numbers from GBD 2
Modified the previous formula (only men in England) to apply to all the data set and generate population numbers  for male and females in England and Greater London

##Generate a data frame with population numbers for England and Greater London (for life table and Dismod II collection). 
##These are derived from total number of cases and rates per 100,000. To derive values we need to select one cause (E.g. all cause)-does not matter what is chosen.

GBD_England_population_male <- filter(GBDdata, location == "england", measure == "deaths", cause == "all causes", sex == "male", metric == "rate" | metric == "number" ) %>% select(metric, age_cat, val, sex_age_cat)

###Generate population numbers frame males England
 for (i in 1:nrow(GBD_England_population_male)) {
    if (GBD_England_population_male$metric[i] == "number") {
      GBD_England_population_male$val_pop[i] <- GBD_England_population_male$val[i] * 10000/ GBD_England_population_male$val[i + 1]}
   else {GBD_England_population_male$val_pop[i] <- NA}
 }
##Remove rows with zero
GBD_England_population_male <- GBD_England_population_male[!is.na(GBD_England_population_male$val_pop),]

##Last only keep relevant variables

GBD_England_population_male <- filter(GBD_England_population_male) %>% select(age_cat, val_pop)

>>>>

##Generate a data frame with population numbers for England and Greater London (for life table and Dismod II collection). 
##These are derived from total number of cases and rates per 100,000. To derive values we need to select one cause (E.g. all cause)-does not matter what we choose.

###First generate population numbers for England and Greater London and then separate in dataframes
GBD_population <- filter(GBDdata, measure == "deaths", cause == "all causes", metric == "rate" | metric == "number" ) %>% select(metric, age_cat, val, sex_age_cat, location)

###Generate population numbers from GBD data
 for (i in 1:nrow(GBD_population)) {
    if (GBD_population$metric[i] == "number") {
      GBD_population$val_pop[i] <- GBD_population$val[i] * 100000/ GBD_population$val[i + 2]}
   else {GBD_population$val_pop[i] <- NA}
 }
##Remove rows with zero
GBD_population <- GBD_population[!is.na(GBD_population$val_pop),]

##Keep relevant variables

GBD_population <- filter(GBD_population) %>% select(sex_age_cat, val_pop, location)

##Create data frames for Greater London and England population

GBD_population_GL <-  filter(GBD_population, location == "greater london") %>% select(sex_age_cat, val_pop, location)

GBD_population_England <-  filter(GBD_population, location == "england") %>% select(sex_age_cat, val_pop, location)

##Check population total numbers

GreaterLondon <- sum(GBD_population_GL$val_pop)
England <- sum(GBD_population_England$val_pop)
